### 2025-09-22 paper/sec/related-work.tex
updated rel work

\paragraph{Argument mining.}
For over fifteen years the field of NLP has been exploring the problem of argument mining, which involves identifying argumentative structures in text, such as claims, premises, and conclusions, and
mapping them to formal representations~\citep{}. Early work in this area focused on rule-based approaches, while more recent work has leveraged machine learning and deep learning techniques to improve
performance~\citep{}. The field has also focused on defining annotation schemes for the task, such as the Argumentative Zoning framework~\citep{}.
Argument mining remains a challenging task, particularly when it comes to handling implicit arguments and reasoning about the relationships between different argumentative
components~\citep{}. While earlier work focused on specific domains such as legal texts or online resources such as Debatepedia, the community has also started engaging with work that explores the use of argument mining in scientific texts~\citep{liakata2012automatic,...} to better understand the structure of scientific arguments and the relationships between different claims and evidence.

>>>>

\paragraph{Argument mining.}
For over fifteen years the field of NLP has been exploring the problem of argument mining, which involves identifying argumentative structures in text, such as claims, premises, and conclusions, and
mapping them to formal representations~\citep{palau2009argumentation,lippi2015argument}  . Early work in this area focused on rule-based approaches, while more recent work has leveraged machine learning and deep learning techniques to improve
performance~\citep{stab2014identifying,stab2017parsing}. The field has also focused on defining annotation schemes for the task, such as the Argumentative Zoning framework~\citep{teufel2002summarizing,teufel2009towards}.
Argument mining remains a challenging task, particularly when it comes to handling implicit arguments and reasoning about the relationships between different argumentative
components~\citep{}. While earlier work focused on specific domains such as legal texts~\citep{toulmin2003uses} or online resources such as Debatepedia~\citep{cabrio2013natural}, the community has also rapidly engaged with work that explores the use of argument mining in scientific texts~\citep{liakata2012automatic,lauscher2018investigating} to better understand the structure of scientific arguments and the relationships between different claims and evidence.
